---
title: 'Activity: Nuclear Reactors'
author: "Maggie Linn"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(rvest)
library(lubridate)
```

## Scrape the Data 

```{r}
#My code here.... 
page <- "http://en.wikipedia.org/wiki/List_of_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

tableList[[21]]

Japan <- tableList[[21]]

names(Japan)[c(3,4)] <- c("type", "model")

Japan <-
  Japan %>%
  filter(row_number() > 1) %>%
  rename(name = Name, 
         reactor = `UnitNo.`,
         status = Status, 
         netMW = `Net capacity (MW)`,
         construction = `Construction start`,
         operation = `Commercial operation`, 
         closure = Closure) %>%
  mutate(construction = lubridate::dmy(construction), 
         operation = lubridate::dmy(operation),
         closure = lubridate::dmy(closure))

Japan$country <- c('Japan')

```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

The table is tidy because each row is an observation, each column is a variable, the column headers are not values, and more. It is not tidy by the dates, so we have to change the dates so they are tidy. This is different from a tidy table because of the dates, which we are mutating.


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}

Japan %>%
  ggplot(aes(x=construction, y=netMW, color=type)) +
  geom_point()

```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}

tableList[[10]]

China <- tableList[[10]]

names(China)[c(3,4)] <- c("type", "model")

China <-
  China %>%
  filter(row_number() > 1) %>%
  rename(name = Name, 
         reactor = `UnitNo.`,
         status = Status, 
         netMW = `Net capacity (MW)`,
         construction = `Construction start`,
         operation = `Commercial operation`, 
         closure = Closure) %>%
  mutate(construction = lubridate::dmy(construction), 
         operation = lubridate::dmy(operation),
         closure = lubridate::dmy(closure))

China$country <- c('China')

ChinaJapan <-
  China %>%
  full_join(Japan)

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}

ChinaJapan %>%
  ggplot(aes(x=operation, y=name, color=type, points=status)) +
  geom_segment(aes(xend=2022, yend='Zhangzhou'))
```